\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-08 paper/main.tex
minor change to abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning
  libraries~(DLLs), such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of techniques have been recently proposed to
  find those bugs, but the lack of a curated set of reproducible bugs
  in DLLs hinders credible evaluation of testing techniques. We present \tname,
  a database of curated reproducible bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DLL testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DLL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning
  libraries~(DLLs), such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem, but the lack of a curated set of reproducible bugs in DLLs
  hinders credible evaluation of such techniques. We present \tname, a
  database of curated reproducible bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DLL testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DLL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}
